The problem and promise of scale in animal social multilayer networks

### 2020-02-08 paper/manuscript.Rmd
reflow

<!-- nobs 
* common, though at different points - more observations until stabilizing
* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
-->

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately 210 
observations for open and approximately 300 observations for forage (Figure 
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity stabilized 
for all three landcover classes at approximately 200 observations for forest and approximately 300 observations for open and forage landcover types. Connective redundancy increased with increasing number of
observations as individuals became more connected to neighbours in multiple
layers (Figure \@ref(fig:nobs)d). Given the overall trend of these multilayer
metrics stabilizing after a certain number of observations are included, the
results suggest this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing the social dynamics
across contexts. <!-- TODO: I'm not sure this is relevant since this is the main way it is already done, can we make this thought more relevant to picking scales or multilayer networks in general? I think it's important for building robust networks -->

<!-- win  length
* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
* layers are more similarly relevant at high window length
-->

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure \@ref(fig:winlen)b). Individual graph strength and layer relevance
increased for all summer layers as individuals became more connected with
increasing window lengths (Figure \@ref(fig:winlen)a, Figure
\@ref(fig:winlen)b). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
<!-- TODO: ?? -->
<!-- TODO: end with something highlighting this shows it's important to properly define your season -->

<!-- Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance  -->

<!-- win position
* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
* same theme shown in the connective redundancy
* quite variable layer similarity, not sure what to pull out of that one
* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
-->

<!-- Shifting window position results showed increasing layer similarity  -->

**Missing: discussion of window position..**

>>>>

<!-- nobs * common, though at different points - more observations until
stabilizing * we dont see the stabilizing/full plateau for connective redundancy
but appears to be coming.. * still some variability, especially for graph
strength because individuals are differently connected but broad strokes - they
stabilize with more observations -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure
\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing the social dynamics across
contexts. <!-- TODO: I'm not sure this is relevant since this is the main way it
is already done, can we make this thought more relevant to picking scales or
multilayer networks in general? I think it's important for building robust
networks -->

<!-- win  length * increasing window length = increasingly similar layers and
increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons
because seasons are less well defined/include more shoulder seasons * decreasing
graph strength at the upper end of window length in winter showing again
inclusion of more shoulder season * layers are more similarly relevant at high
window length -->
Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure \@ref(fig:winlen)b). Individual graph strength and layer relevance
increased for all summer layers as individuals became more connected with
increasing window lengths (Figure \@ref(fig:winlen)a, Figure
\@ref(fig:winlen)b). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
<!-- TODO: ?? --> <!-- TODO: end with something highlighting this shows it's
important to properly define your season -->
<!-- Similarly, shifting window position of the summer season resulted in an
increase in number of connections between individuals. Layer relevance  -->
<!-- win position * increasing network connectivity in summer when the window
position is moved - these seasons are more similar than the original window
position * same theme shown in the connective redundancy * quite variable layer
similarity, not sure what to pull out of that one * increased graph strength for
winter down the middle, with generally increasing summer layers - again where
the season is including more shoulder season potentially -->
<!-- Shifting window position results showed increasing layer similarity  -->
**Missing: discussion of window position..**
